---
title: "FibonacciBases"
author: "Kyoko Sano"
output: html_document
---

First, read in the fibonaccibases.csv file generated using the Python program.
```{r}
df.fib <- read.csv("fibonaccibases.csv")
```

This data is obviously representing the exponential graph.
```{r}
plot(df.fib$base, df.fib$total.possible.pairs, main = "Number of Permutations of a Pair of Integers in the One's Place of a Base",xlab="Base", ylab='Possible Pairs')
```


This one is quite messy on screen. Perhaps, plotting the bases’ data points by multiples may provide more information.
I will come back to this later.
```{r}
plot(df.fib$base, df.fib$sequence.length, main = "Sequence Lengths", xlab="Base", ylab="Seq Length")
```


This density plot shows the majority of the Fibonacci sequence lengths are under 1000. In fact, the median is 708.
```{r}
plot(density(df.fib$sequence.length), main = "Density Distribution of Sequence Lengths", xlab = "Length of Sequence", ylab = "Density")
```

Let’s work with the top portion of the dataset.
```{r}
plot(df.fib$base[1:60], df.fib$sequence.length[1:60], main = "Sequence Lengths (shorter)", xlab="Base", ylab="Seq Length")
```


It looks like the reverse version of the height of a ball as it bounces closer and closer to the ground with more time. Here, the sequence lengths show a gradual increase as well as an increase in the fluctuation between the sequence lengths of consecutive bases.

My next steps would be to find relations between the bases of similar sequence lengths and build a model to represent this data.